\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

\begin{itemize}
	\item Demo dummy data for the teams (id, name, division, etc) (maybe availability preferences)
	\item Demo dummy data for fields (location + time)
	\item Demo the scheduling algorithm (pseudocode/possbibly)
	\item Demo front end tha displays the schedule.
\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Damien Cheung & 2\\
Jad Haytaoglu & 2\\
Derek Li & 2\\
Temituoyo Ugborogho & 1\\
Emma Wigglesworth & 2\\
\bottomrule
\end{tabular}
\end{table}

The team does not have a lot of team meetings recorded dues to the casual nature
of the a large majority of meetings. A lot of brainstorming and work was done 
in a study group setting. We also did not have the GitHub set up early on, so some
early meetings were not recorded. Moving forward, the team will record more of the
team gatherings.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Damien Cheung & 1\\
Jad Haytaoglu & 1\\
Derek Li & 0\\
Temituoyo Ugborogho & 1\\
Emma Wigglesworth & 1\\
\bottomrule
\end{tabular}
\end{table}

The professor that we are working with, is more of a stakeholder as he has informed
us that he will not be providing technical support for the development of the product.
Due to the reason, we limited our contact to information gathering till prototypes are
involved, then we will be having more meetings with the professor.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Damien Cheung & 1\\
Jad Haytaoglu & 0\\
Derek Li & 0\\
Temituoyo Ugborogho & 0\\
Emma Wigglesworth & 3\\
\bottomrule
\end{tabular}
\end{table}

The team started the recording of lectures a lot later, so we have a lot of lecture sessions
that were not included, this is why we have a really low number for the total number of 
lectures attended.

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Damien Cheung & 2\\
Jad Haytaoglu & 2\\
Derek Li & 1\\
Temituoyo Ugborogho & 1\\
Emma Wigglesworth & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 128 & 100\% \\
Damien Cheung & 29 & 22.66\% \\
Jad Haytaoglu & 24 & 18.75\% \\
Derek Li & 31 & 24.22\% \\
Temituoyo Ugborogho & 10 & 7.81\% \\
Emma Wigglesworth & 34 & 26.56\% \\
\bottomrule
\end{tabular}
\end{table}


\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Damien Cheung & 16 & 15 \\
Jad Haytaoglu & 9 & 9 \\
Derek Li & 5 & 4 \\
Temituoyo Ugborogho & 9 & 8 \\
Emma Wigglesworth & 23 & 22 \\
\bottomrule
\end{tabular}
\end{table}

\section{CICD}

CI/CD will be used in a few way throughout this project. It will beused for 
the automation of our tests, simplification of our integration, improving the
speed of our deployment, and also enhancing collaboration between team members.
As mentioned in the development plan, a major use of CI in our project will be 
to ensure that new code doesn't break existing functionality or introduce bugs
to our codebase. This a huge addition to our teams' developments process, 
considerably improving our teams' productivity.

\end{document}